%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}

\name{Pranav Ravichandran} % Your name
\address{\textit{Chennai, India.} \\ \textit{{\href{mailto:me@onloop.net}{me@onloop.net}}} \\ \textit{{\href{http://onloop.net}{http://onloop.net}}}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf St. Joseph's College of Engineering, Anna University} \hfill {\em 2009-2013} \\
Bachelor of Engineering in Electrical and Electronics Engineering \\
CGPA: 7.44/10

{\bf {\href{http://onloop.net/hairyplotter/}{Thesis, Final year}}} \hfill {\em 2013} \\
Human-Computer interface with Electrooculogram-based eye gesture detection and classification.

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, Common Lisp, C, Java, JavaScript \\
Environment & Unix, Emacs, Bash, Git, Make/Cmake, Valgrind, Nginx \\
The Web & HTML, CSS, Django, Node.js, jQuery, Backbone.js \\
Databases & PostgreSQL, MongoDB
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{\href{https://www.google-melange.com/gsoc/project/details/google/gsoc2011/pranavrc/5757334940811264}{Google Summer of Code, Google}}{Apr - Sep 2011}{Student Contractor}{Remote}
\item Implemented improvements and fixes to SMARTS, a Game Artificial Intelligence library for KDE Gluon.
\item Integrated SMARTS into KDE Gluon, giving it the capabilities of a Behavior Tree system.
\item Developed a KPart GUI to plug the SMARTS Behavior Tree editor into Gluon.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{\href{https://happyfox.com/}{HappyFox, Tenmiles}}{January 2014 - Present}{Software Developer}{Chennai, India}
\item Implementing features, enhancements and integrations for HappyFox and related components.
\item Developed a decoupled REST-based task-server with Celery and RabbitMQ, to handle deferred services.
\item Implemented Contextual Search for Knowledge Base Articles using Latent Semantic Analysis.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{National Institute of Information Technology}{2009}{Computer (A+) and Network (N+) Technician Certification.}{Chennai, India}
\item Completed hands-on courses as Computer Technician (60 hours) and Network Technician (48 hours).
\end{rSubsection}

\end{rSection}

%-------------------------------------------------
% OPEN SOURCE CONTRIBUTIONS
%-------------------------------------------------

\begin{rSection}{Open Source Contributions}

\begin{rSubsection}{\href{https://bugzilla.mozilla.org/user\%5Fprofile?user\%5Fid=431664}{Mozilla}}{2012-2013}{}{}
\item Developed a Code Commenting and Uncommenting feature for the Mozilla Firefox Source Editor.
\item Implemented W3C spec restrictions on WebIDL dictionary member types.
\item Contributed other patches and bugfixes.
\end{rSubsection}

\begin{rSubsection}{\href{https://github.com/mdoege/PySynth/commits?author=pranavrc}{PySynth}}{July 2012}{}{}
\item Created an interactive Command Line Interpreter to parse Musical Notation and render tunes on the fly.
\item Implemented multi-library support for audio playback.
\end{rSubsection}

\end{rSection}

%--------------------------------------------------
% INDEPENDENT PROJECTS
%--------------------------------------------------

\begin{rSection}{{\href{http://github.com/pranavrc/}Independent Projects}}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\href{http://onloop.net/transit/}{Transit.js} & A JavaScript library to create purely client-side, interactive transit maps. \\
\href{http://u.onloop.net/}{Suburl} & A placeholder substitution-based URL shortener and sanitizer in Common Lisp. \\
\href{http://this.onloop.net/}{This.onloop} & Music Search and Album discovery tool, using Common Lisp and Restas. \\
\href{http://redd.it/1i7lh3}{Howstat} & Resident player-statistics lookup bot for Reddit's Cricket Community, /r/Cricket. \\
\href{http://music.onloop.net}{PDoS} & An exercise in extrapolating algorithmic patterns to musical notes. \\
\href{http://github.com/pranavrc/}{Others} & \href{http://github.com/pranavrc/}{http://github.com/pranavrc/}
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
