%%%%%%
% Pranav Ravichandran - curriculum vitae
% Edited using emacs and texlive
% Uses LaTeX and moderncv
%%%%%%

\documentclass[10pt,a4paper]{moderncv}
\usepackage{url}
\usepackage{footmisc}
%\usepackage{verdana}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.8]{geometry} % adjust the page margins

\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Pranav}
\familyname{Ravichandran}
%\title{Resume.}
\address{Address Line 1,\\Address Line 2}{.}
\phone{9876543210}
\email{me@onloop.net}
\homepage{www.onloop.net}
% \photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;
\quote{Application for the role of Software Engineer.}
% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle

\section{Technical Skills}
\cvcomputer
{\textbf{OS}}{Linux, Windows}
{\textbf{Languages}}{Python, C, C++, Java, JavaScript}
\cvcomputer
{\textbf{Tools}}{Vim, bash, git,\\make/cmake, valgrind, Photoshop}
{\textbf{Web Dev}}{HTML5, CSS, AJAX, \\Flask, jQuery}
\cvcomputer
{\textbf{Frameworks}}{Qt, Orion, libsndfile, PortAudio}
{\textbf{Mobile}}{Android}
{}{}

% --------------------------------------
% WORK EX
% --------------------------------------

\section{Work Experience}

\cventry{Apr - Sep 2011}{{\href{http://www.google-melange.com/gsoc/project/google/gsoc2011/pranavrc/20001}{Google Summer of Code 2011}}}{Student Contractor}{Google}{}{Integrated SMARTS, a Game Artificial Intelligence Framework into KDE Gluon, and also implemented a KPart Graphical User Interface to plug the SMARTS Editor into Gluon.}

%%\pagebreak

\section{Open Source Contributions}

\cventry{Jan 2012 onwards}{{\href{http://hg.mozilla.org/mozilla-central/log?rev=pranav+ravichandran}{Mozilla}}}{}{}{}{
\begin{itemize}
{\item{Developed a Code Commenting/Uncommenting feature for the Mozilla Firefox Source Editor.}}
{\item{Implemented a mechanism to hide unused services from the Firefox Preferences UI.}}
{Other minor patches.}
\end{itemize}
}

\cventry{July 2012}{{\href{http://github.com/mdoege/PySynth/commits/master}{PySynth}}}{}{}{}{Created an interactive Command Line Interpreter to parse Musical Notation and render tunes, aiding in on-the-fly notational composition with PySynth, and also implemented support for audio playback.}

% --------------------------------------
% PROJECTS
% --------------------------------------

\section{Independent Projects}

\cvlistitem
{\textbf{PDoS} -- {{\href{http://music.onloop.net/}{\small http://music.onloop.net/}}}
  \\Patterned Disruption of Silence - An exercise in extrapolating algorithmic patterns to musical notes, with C, libsndfile and PortAudio.}

\cvlistitem
{\textbf{Album.onloop} -- {{\href{http://album.onloop.net/}{\small http://album.onloop.net/}}}
  \\Music Album discovery tool and review aggregator, using Python, Flask, jQuery, HTML5, CSS and JSON.}

\cvlistitem
{\textbf{SC-ircle} -- {{\href{http://soundcloud.onloop.net/}{\small http://soundcloud.onloop.net/}}}
  \\A Python/jQuery webapp to find out who among a Soundcloud user's followees aren't following them back, well-received by the spam-hit Soundcloud user community.}

\cvlistitem
{\textbf{Strand} -- {{\href{http://devlog.onloop.net}{\small http://devlog.onloop.net/}}}
  \\A minimal Content Publishing System written in Python, with support for CLI blogging.}

\cvlistitem
{\textbf{Bookinate} -- {{\href{http://onloop.net/bookinate}{\small http://onloop.net/bookinate/}}}
  \\JS App to convert text and HTML content into flip-book format using turn.js.}

\cvlistitem
{\textbf{Pnoesis}
  \\Language mapping experiments in C, using regex and lexMap, a homebrew keymapper in C.}

\cvlistitem
{\textbf{Post}
 \\Android app to send custom HTTP POST requests to a server.\\\\ - These and other projects at {\href{http://github.com/pranavrc}{http://github.com/pranavrc/}}}


% --------------------------------------
% Courses
% --------------------------------------
%\section{Courses}
%\cvlistdoubleitem{Database Management Systems}{Operating Systems}
%\cvlistdoubleitem{Algorithms}{Artificial Intelligence}
%%\pagebreak
\section{Education}
\cventry{Aug 2009 - May 2013}{B.E. Electrical and Electronics.}{Foo University, Foo}{}{}{Completed 7 out of 8 Semesters - \textit{CGPA $7.0$/$10.0$}.}
% --------------------------------------
% INTERESTS HOBBIES
% --------------------------------------

% --------------------------------------
% FOOTNOTES
% --------------------------------------
\end{document}
